---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geschaeftsberichtApp

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/ogdtg/geschaeftsberichtApp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ogdtg/geschaeftsberichtApp/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `geschaeftsberichtApp` package powers the interactive dashboard accompanying the *Statistischer Anhang* of the **Geschäftsbericht des Kantons Thurgau**. It provides a dynamic, filterable, and downloadable interface for exploring official statistical tables.

## ✨ Features

- View all tables published in the printed *Geschäftsbericht* in a modern interactive dashboard
- Link directly from the printed table to its digital counterpart
- Render tables with grouped headers using `flextable`
- Download individual tables as Excel files
- Download complete time series across all years in multiple formats

## Installation

You can install the development version of geschaeftsberichtApp like so:

``` {r, eval = FALSE}
devtools::install_github("ogdtg/geschaeftsberichtApp")
```

## Run the app


After successfull installation, you can run the app by using the following code:

``` {r, eval = FALSE}
library(geschaeftsberichtApp)
geschaeftsberichtApp::run_a
```

